### 2022-04-25 background.tex
Update voicefilter description

Also, permutation invariant training (PIT) in~\cite{PIT}, which is widely used in blind speaker separation.
One big problem of speaker independent speech separation is the permutation of the output of the network.
PIT solves this problem, which outputs all the permutations and using the smallest mean squared error (MSE) as the optimization goal.
PIT structure is as figure~\ref{fig:PIT_structure}.
To better solve the issue of tracking the speaking person, one utterance-level algorithm uPIT in~\cite{uPIT} is proposed.
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{img/PIT_structure}
    \caption{Permutation invariant training structure}
    \label{fig:PIT_structure}
\end{figure}

To better solve the disadvantages of deep clustering, a new deep embedding clustering based algorithm DEF-DL~\cite{DEF-DL} is proposed.
DEF-DL uses supervised network to replace of K-means clustering algorithm, and use this feature as the input of uPIT network to separate speech.
The whole structure is as figure~\ref{fig:def_dl_structure}.
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.6\textwidth]{img/DEF-DL_structure}
    \caption{DEF-DL structure}
    \label{fig:def_dl_structure}
\end{figure}

>>>>

Also, permutation invariant training (PIT) in~\cite{PIT}, which is widely used in blind speaker separation.
One big problem of speaker independent speech separation is the permutation of the output of the network.
PIT solves this problem, which outputs all the permutations and using the smallest mean squared error (MSE) as the optimization goal.
PIT structure is as figure~\ref{fig:PIT_structure}.
To better solve the issue of tracking the speaking person, one utterance-level algorithm uPIT in~\cite{uPIT} is proposed.
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{img/PIT_structure}
    \caption{Permutation invariant training structure~\cite{PIT}}
    \label{fig:PIT_structure}
\end{figure}

To better solve the disadvantages of deep clustering, a new deep embedding clustering based algorithm DEF-DL~\cite{DEF-DL} is proposed.
DEF-DL uses supervised network to replace K-means clustering algorithm, and use this feature as the input of uPIT network to separate speech.
The whole structure is as figure~\ref{fig:def_dl_structure}.
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.6\textwidth]{img/DEF-DL_structure}
    \caption{DEF-DL structure~\cite{DEF-DL}}
    \label{fig:def_dl_structure}
\end{figure}
For the target speaker separation, one classic structure is speaker encoder, speech encoder, separator, decoder framework, as shown in figure~\ref{fig:enc_sep_doc_arc}.

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.7\textwidth]{img/voicefilter_struct}
    \caption{VoiceFilter structure~\cite{voicefilter}}
    \label{fig:voicefilter_struct}
\end{figure}

One example is VoiceFilter~\cite{voicefilter}, the structure is shown in figure~\ref{fig:voicefilter_struct}.
The speaker encoder is trained separately to get the speaker embedding.
For each iteration of training, the noisy audio, clean audio and reference audio are given.
Operating Short-time Fourier transform (STFT) to both noisy audio and clean audio to get the magnitude spectrogram and phase spectrogram.
The magnitude spectrogram of the noisy audio is fed into the separator, for VoiceFilter, it is Convolutional Neural Network (CNN), Long short-term memory (LSTM)~\cite{LSTM} and fully-connected layer.
After the separator predicting the mask, dot multiplication is applied to the input magnitude spectrogram to get the predicted masked magnitude spectrogram.
Last, applying inverse STFT to the masked magnitude spectrogram and the original phase spectrogram to get the enhanced audio.
The training loss of the network is mean squared error (MSE) between the masked magnitude spectrogram and the clean spectrogram from the clean audio.
